%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING--------------------
\begin{flushright}
  \vspace{-4pt}
  \color{gray}
  \item
  Last Updated on \today 
\end{flushright}

\vspace{-7pt}

\begin{center}
    \textbf{\Large \scshape Cole Rottenberg } \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/colerottenberg}{\underline{github.com/colerottenberg}} $  $
    % \faIcon{code}
    % \href{https://www.johndoe.com}
    % {\underline{johndoe.com}} $  $
    \faIcon{linkedin}
    \href{https://linkedin.com/in/cole-rottenberg}{\underline{linkedin.com/in/colerottenberg}} $  $
    \faIcon{envelope}
    \href{mailto:cole.rottenberg@gmail.com}
    {\underline{cole.rottenberg@gmail.com}}
\end{center}

\section{Professional Summary}
  \resumeSubHeadingListStart

    % Professional Summary
    \resumeSubheading
      {}{}
      {}{}
      \vspace{-30pt}
      \resumeItemListStart
        Senior in college majoring in Computer Engineering, showcasing a fervent interest in systematic trading.  
        Proficient programming skills, with proven track record in project management. Actively engaged in clubs and organizations to cultivate both hard and soft skills essential to the industry. 
        Eager to leverage academic excellence and hands on experience in a dynamic and innovative professional setting.
      \resumeItemListEnd

    \vspace{-10pt}

  \resumeSubHeadingListEnd

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Florida}{December 2024}
      {Bachelor of Science in Computer Engineering}{Current GPA: 3.52/4.0}
      
    \resumeSubheading
      {Lake Highland Preparatory School }{June 2020}
      {}{GPA: 4.3/4.0}

    \vspace{-10pt}

  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: C/C++, Python, \LaTeX, SQL, Go, Rust } \\
     
     % \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, FreeRTOS, ESP-IDF}
     
    }}
 \end{itemize}

% -------------------- PROJECTS --------------------
\section{Technical Projects}
    \resumeSubHeadingListStart
    
        \resumeProjectHeading
        {\textbf{Real-time IMU Data Streaming via DMA \& UART} $|$ \footnotesize\emph{C, C++, ASM}}{May 2023}
        \resumeItemListStart
            \resumeItem{Enable low latency access to IMU data through DMA coprocessor freeing CPU}
            \resumeItem{Ran CPU in sync with software enabled DMA transfers}
            % \resumeItem{Used minimal API calls, the bulk of the code was self-made logic and design}
            % \resumeItem{Chose to restart the entire project to optimize runtime and experience}
            \resumeItem{Redesigned data transfers architecture allowing an order of magnitude increase in speed}
            \resumeItem{Pipelined IMU data over high-speed UART stream via hardware interrupts}
            % \resumeItem{Optimized UX (User Experience) e.g. bought a simple domain name, made documentation, recorded a setup \& demo video, customization through URL arguments}
            % \resumeItem{Published to GitHub and obsproject.com}
        \resumeItemListEnd
          
        \resumeProjectHeading
        {\textbf{Multi-Trend Following Strategy} $|$ \footnotesize\emph{Python, NumPy, Pandas, Matplotlib}}{October 2023}
        \resumeItemListStart
            \resumeItem{Developed a strategy in Python,  leveraging libraries such as Pandas for data manipulation and NumPy for numerical computations. Implemented algorithmic trading models to identify and follow profitable trends. }
            % \resumeItem{Created intended behavior by making logic complying to the extensive Spigot API in Java}
            \resumeItem{Enhanced the original model by integrating advanced statistical methods for more accurate trend prediction and risk management.}
            \resumeItem{Worked closely with front-end developers to ensure seamless data integration and back-end project management matched front-end. }
            \resumeItem{Published to GitHub}
            % \resumeItem{Published to GitHub and spigotmc.org}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

        \resumeProjectHeading
          {\textbf{AlgoGators} $|$ \footnotesize\emph{Assistant Portfolio Manager}}{August 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed and deployed a comprehensive Python-based application for
            divergent strategies, integrating SQL server for futures data
            retrieval across 100+ instruments. Implemented advanced analytics
            using exponentially weighted moving averages to generate trading
            signals, and designed dynamic optimization algorithms for
            capital-efficient position management.}
            \resumeItem{Successfully automated signal generation using cron and played a key role in system deployment on a remote server, enhancing operational efficiency and decision-making in trading strategies.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Florida Cryptocurrency and Alternative Assets Club} $|$ \footnotesize\emph{Treasurer}}{Jan. 2022 -- Dec. 2023}
          \resumeItemListStart
            \resumeItem{Lead topic discussions on the cutting edge applications and research within blockchain research}
            \resumeItem{Host guest speakers from the industry}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Blue Vigil} $|$ \footnotesize\emph{Intern}}{June 2023 -- August 2023}
          \resumeItemListStart
            \resumeItem{Developed communication protocols for data transfer over RS-485 in electrically noisy environments. Implemented Reed
            Solomon Error-correction code alleviating communication faults due to corruption.}
            \resumeItem{Built fault warning systems within
            commercial drone lighting system on ESP-32s}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd 

\end{document}

