\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\geometry{letterpaper, margin=1in}

\begin{document}
\sloppy

\begin{center}
  \Large Cole H. Rottenberg
\end{center}


Dear Hiring Manager,
\vspace*{10pt}

I am writing to express my keen interest in the internship with algorithm development at Hudson River Trading. As a dedicated Computer Engineering student at the University of Florida with a passion for systematic trading, I am excited about the opportunity to contribute to your team and further develop my skills in a dynamic and innovative environment.

\par
During my academic career, I have developed a strong foundation in data science and machine learning, along with software and hardware engineering skills. This unique blend of knowledge has been instrumental in my role as an Assistant Portfolio Manager with AlgoGators, a university-affiliated systematic trading club. Managing divergent strategies within our \$500,000 portfolio, I have not only developed a knack for identifying market trends but also an understanding of applying theoretical concepts in a practical, results-oriented setting. My experience embedding these strategies into an automated system that analyzes daily market data and portfolio has been both challenging and rewarding, invoking my passion for this field.
\par
Last Summer, I expanded my technical expertise through an engineering internship focused on embedded systems at a growing autonomous aerial vehicle company. I reported directly to the CEO and my responsibilities included: implementing a new flight control system, implementing a noise reduction algorithm. This experience further enhanced my project management, problem-solving, and programming skills while excelling in fast-paced, resulting in an offer for future employment.
\par

What draws me to Hudson River Trading is the prospect of engaging in experimental research with the extensive datasets. The opportunity to explore such rich resources and contribute to groundbreaking financial strategies is the dynamic learning experience I am seeking. I am particularly interested in how my background in systematic trading and data-driven decision-making can be applied to HRT's innovative approaches in the financial markets.
\par
Thank you for considering my application. I am confident that my blend of academic knowledge, practical experience, and enthusiasm will be a positive contribution to your team. I am eager to pursue an intership with HRT, as I believe it will offer an opportunity for both personal and professional growth. I look forward to meeting with you in the future to further discuss my qualifications for a position as a intern at Hudson River Trading this upcoming summer. If you have any questions, please feel free to email me at \href{mailto:cole.rottenberg@gmail.com}{cole.rottenberg@gmail.com} or call me at \href{tel:+1-407-961-0600}{407-961-0600}.

Sincerely,

Cole Rottenberg

\end{document}