\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{letterpaper, margin=1in}

\begin{document}
\begin{letter}{Hiring Manager's Name \\
Voloridge Investment Management \\
Address Line 1 \\
Address Line 2}

\opening{Dear Hiring Manager,}

I am writing to express my keen interest in the Research Intern position at Voloridge Investment Management.
As a dedicated Computer Engineering student at the University of Florida with a passion for systematic trading, I am excited about the opportunity to contribute to your team and further develop my skills in a dynamic and innovative environment.

During my academic career, I have developed a strong foundation in data
science and machine learning, along with software and hardware engineering
skills.
This unique blend of knowledge has been instrumental in my role as an
Assistant Portfolio Manager with AlgoGators, a university-affiliated
systematic trading club.
Managing divergent strategies within our \$500,000 portfolio, I have not
only developed a knack for identifying
market trends but also an understanding of applying theoretical
concepts in a practical, results-oriented setting.
My experience embedding these strategies into an automated system that
analyzes daily market data and portfolio has been both challenging and rewarding,
invoking my passion for this field.

Last Summer, I expanded my technical expertise through an
engineering internship focused on embedded systems at a growing
autonomous aerial vehicle company. I reported directly to the CEO and my
responsibilities included:
implementing a new flight control system, implementing a noise reduction
algorithm
This experience further enhanced my project management, problem-solving,
and programming skills while excelling in fast-paced, resulting in an
offer for future employment.

What draws me to Voloridge Investment Management is the prospect of
engaging in experimental research with the extensive datasets.
The opportunity to explore such rich resources and contribute to
groundbreaking financial strategies is the dynamic learning experience I
am seeking. I am particularly interested in how my background in
systematic trading and data-driven decision-making can be applied to
Voloridge's innovative approaches in the financial markets.

Thank you for considering my application. I am confident that my blend
of academic knowledge, practical experience, and enthusiasm will be a
positive contribution to your team. I am eager to pursue an intership
with Voloridge, as I believe it will offer an opportunity for both
personal and professional growth. I look forward to meeting with you in
the future to further discuss my qualifications for a position as a
Research Intern at Voloridge this upcoming summer. If you have any
questions, please feel free to email me at
\href{mailto:cole.rottenberg@gmail.com}{cole.rottenberg@gmail.com}
or call me at \href{tel:+1-407-961-0600}{407-961-0600}.

\closing{Sincerely,\\[1\baselineskip]
Cole Rottenberg}

\end{letter}
\end{document}